Fast Automatic Bayesian Cubature Using Lattice Sampling

### 2019-08-17 Submission_Jul29/BayesianCubaturePaper_Jul29_Fred_Jagadees - Rev1c - submission.tex
fix typos

% This is a general template file for the LaTeX package SVJour3
% for Springer journals. Original by Springer Heidelberg, 2010/09/16
%
% Use it as the basis for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
\RequirePackage{amsmath}
\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
%\usepackage{cite}
%
% insert here the call for the packages your document requires
%\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%\usepackage{latexsym}
% etc.
%
% Jag's 
\usepackage{tabu}
\usepackage{cancel}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
%\usepackage[caption=false]{subfig}
\usepackage{subcaption}
\usepackage{booktabs, mathtools}
\usepackage[dvipsnames]{xcolor}
\usepackage{url}
\usepackage[titletoc,title]{appendix}
%\usepackage{refcheck}  % points out unused labels, refs ...
\usepackage[htt]{hyphenat}

@@

        \State\label{LoopStart}Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
        \State Compute $\vtheta$ by \eqref{eqn:thetaMLE} or \eqref{vthetaGCV}
        \State Compute $\err_{\textup{CI}}$  according to \eqref{eqn:err_MLEGCV} or \eqref{FJH:eq:errFull}

@@

\begin{theorem} \label{thm:fastparam}
Under assumptions \eqref{fastcompAssump}, the parameters and credible interval half-widths in Theorem \ref{thm:param} may be expressed in terms of the fast Bayesian transforms of the integrand data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
\begin{align}
\nonumber
m_\MLE &=  m_{\full} = m_{\GCV} =  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
\\
\nonumber
s^2_\MLE 
& =
\frac{1}{n^2} 
\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}, \\
\nonumber
\widehat{\sigma}^2_{\textup{full}}
& =
\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
\times
\left[\frac{\lambda_1}{n}{\left(1 - \frac{\widetilde{c}_1}{\lambda_1}\right)^2} + \left(c_0  - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i}\right) \right], \\
\nonumber 
s^2_{\textup{GCV}} & =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1},
\end{align}
\begin{subequations}
\label{fastTheta}
\begin{align}
\label{eqn_MLE_loss_func_optimized_2}
\vtheta_\MLE
&= 
\argmin_{\vtheta}
\left[
\log\left(
\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}}
\right) 
 + \frac{1}{n}\sum_{i=1}^n \log(\lambda_{\vtheta,i})
\right],\\
\label{thetaGCV} 
\vtheta_{\GCV} 
&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}^2} 
\right)  
-2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta, i}} \right)
\right], 
\end{align}
\end{subequations}
\begin{align}
\nonumber
\hmu_\MLE  &= \hmu_{\full} = \hmu_{\GCV} =
\frac{\widetilde{y}_1}{n} +
\frac 1n \sum_{i=2}^n \frac{ \widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}, \\
\nonumber
\err_\MLE  &
=
\frac{2.58}{n}\sqrt{
	\sum_{i=2}^{n} \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  
	\,
	\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
}, \\
\nonumber
\err_{\full} & = t_{n-1,0.995} \hsigma_{\textup{full}}, \\
\nonumber
\err_{\textup{GCV}} & =
\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
\right\}^{1/2}.
\end{align}
Under the further assumption \eqref{addAssump}, it follows that 
\begin{equation}
\label{muhatGCV-FB-MLE-Simple}
\hmu_\MLE  = \hmu_{\full} = \hmu_{\GCV} =
\frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
\end{equation}
and so $\hmu$ is simply the sample mean.  Also, under assumption \eqref{addAssump}, the credible interval half-widths simplify to
\begin{subequations}
\label{errSimple}
\begin{align}
\label{eq:errMLEAllAsump}
\err_\MLE  &
=
\frac{2.58}{n}\sqrt{
	\sum_{i=2}^{n} \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  
	\,
	\left( 1 -  \frac{n}{\lambda_1} \right) 
}, \\
\label{FJH:eq:errFullSimple}
\err_{\textup{full}}
&=
t_{n-1,0.995}
\sqrt{\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  \left(\frac{\lambda_1}{n}  - 1  \right)}, \\
\nonumber
\err_{\textup{GCV}} & =
\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
\left( 1 -  \frac{n}{\lambda_1} \right)  
\right\}^{1/2}. \label{errGCVSimple}
\end{align}
\end{subequations}
In the formulas for the credible interval half-widths, $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
\end{theorem}

@@

		\State\label{LoopStart}Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
		\State Compute $\vtheta$ by \eqref{eqn_MLE_loss_func_optimized_2} or \eqref{thetaGCV}
		\State Compute $\err_{\textup{CI}}$  according to \eqref{fastStoppingCriterionMLE}, \eqref{fastStoppingCriterionFull}, or \eqref{fastStoppingCriterionGCV}

>>>>

% This is a general template file for the LaTeX package SVJour3
% for Springer journals. Original by Springer Heidelberg, 2010/09/16
%
% Use it as the basis for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
\RequirePackage{amsmath}
\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
%\usepackage{cite}
%
% insert here the call for the packages your document requires
%\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%\usepackage{latexsym}
% etc.
%
% Jag's 
\usepackage{tabu}
\usepackage{cancel}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
%\usepackage[caption=false]{subfig}
\usepackage{subcaption}
\usepackage{booktabs, mathtools}
\usepackage[dvipsnames]{xcolor}
\usepackage{url}
\usepackage[titletoc,title]{appendix}
%\usepackage{refcheck}  % points out unused labels, refs ...
% \usepackage[htt]{hyphenat}

@@

        \State Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
        \State Compute $\vtheta$ by \eqref{eqn:thetaMLE} or \eqref{vthetaGCV}
        \State Compute $\err_{\textup{CI}}$  according to \eqref{eqn:err_MLEGCV} or \eqref{FJH:eq:errFull}

@@

\begin{theorem} \label{thm:fastparam}
Under assumptions \eqref{fastcompAssump}, the parameters and credible interval half-widths in Theorem \ref{thm:param} may be expressed in terms of the fast Bayesian transforms of the integrand data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
\begin{align}
\nonumber
m_\MLE &=  m_{\full} = m_{\GCV} =  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
\\
\nonumber
s^2_\MLE 
& =
\frac{1}{n^2} 
\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}, \\
\nonumber
\widehat{\sigma}^2_{\textup{full}}
& =
\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
\times
\left[\frac{\lambda_1}{n}{\left(1 - \frac{\widetilde{c}_1}{\lambda_1}\right)^2} + \left(c_0  - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i}\right) \right], \\
\nonumber 
s^2_{\textup{GCV}} & =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1},
\end{align}
\begin{subequations}
\label{fastTheta}
\begin{align}
\label{eqn_MLE_loss_func_optimized_2}
\vtheta_\MLE
&= 
\argmin_{\vtheta}
\left[
\log\left(
\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}}
\right) 
 + \frac{1}{n}\sum_{i=1}^n \log(\lambda_{\vtheta,i})
\right],\\
\label{thetaGCV} 
\vtheta_{\GCV} 
&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}^2} 
\right)  
-2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta, i}} \right)
\right], 
\end{align}
\end{subequations}
\begin{align}
\nonumber
\hmu_\MLE  &= \hmu_{\full} = \hmu_{\GCV} =
\frac{\widetilde{y}_1}{n} +
\frac 1n \sum_{i=2}^n \frac{ \widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}, \\
\nonumber
\err_\MLE  &
=
\frac{2.58}{n}\sqrt{
	\sum_{i=2}^{n} \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  
	\,
	\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
}, \\
\nonumber
\err_{\full} & = t_{n-1,0.995} \hsigma_{\textup{full}}, \\
\nonumber
\err_{\textup{GCV}} & =
\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
\right\}^{1/2}.
\end{align}
Under the further assumption \eqref{addAssump}, it follows that 
\begin{equation}
\label{muhatGCV-FB-MLE-Simple}
\hmu_\MLE  = \hmu_{\full} = \hmu_{\GCV} =
\frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
\end{equation}
and so $\hmu$ is simply the sample mean.  Also, under assumption \eqref{addAssump}, the credible interval half-widths simplify to
\begin{subequations}
\label{errSimple}
\begin{align}
\label{eq:errMLEAllAsump}
\err_\MLE  &
=
\frac{2.58}{n}\sqrt{
	\sum_{i=2}^{n} \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  
	\,
	\left( 1 -  \frac{n}{\lambda_1} \right) 
}, \\
\label{FJH:eq:errFullSimple}
\err_{\textup{full}}
&=
t_{n-1,0.995}
\sqrt{\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  \left(\frac{\lambda_1}{n}  - 1  \right)}, \\
\label{errGCVSimple}
\err_{\textup{GCV}} & =
\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
\left( 1 -  \frac{n}{\lambda_1} \right)  
\right\}^{1/2}. 
\end{align}
\end{subequations}
In the formulas for the credible interval half-widths and $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
\end{theorem}

@@

		\State Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
		\State Compute $\vtheta$ by \eqref{eqn_MLE_loss_func_optimized_2} or \eqref{thetaGCV}
		\State Compute $\err_{\textup{CI}}$  according to \eqref{fastStoppingCriterionMLE}, \eqref{fastStoppingCriterionFull}, or \eqref{fastStoppingCriterionGCV}
